Case Study: 16S microbiome data (ENIGMA)

### 2018-04-03 datasets/microbiome/microbiome-enigma.Rmd
Move enigma data to dropbox

## project data/results folders
datdir <- "DATA"
resdir <- "RESULTS"
enigma_dir <- "enigma"

@@

al_result_file <- file.path(resdir, "enigma-al-otus-results.rds")
al_bench_file <- file.path(resdir, "enigma-al-otus-benchmark.rds")

```

@@

```{r, enigma-readdata}
## load OTU table and metadata
# Note to others: not sure why read.table breaks on this file.
otu <- read.table(file.path(datdir, enigma_dir, 
                            "otu_table_resampled_updated_r.txt"), 
                  sep='\t', header = TRUE, row.names = 1)
meta <- read.csv(file.path(datdir, enigma_dir, "metadata.txt"), sep='\t')

>>>>

## project data/results folders
datdir <- "data"
resdir <- "results"
enigma_dir <- file.path(datdir, "enigma_results")

@@

al_result_file <- file.path(resdir, "enigma-al-otus-results.rds")
al_bench_file <- file.path(resdir, "enigma-al-otus-benchmark.rds")
```

@@

We download the data from Dropbox if not already available.

```{r, enigma-download-data}
if (!file.exists(file.path(enigma_dir, "enigma.metadata.txt"))) {
    download.file("https://www.dropbox.com/s/0r1zjp26u10l0p4/enigma.metadata.txt?dl=1",
                  destfile = file.path(enigma_dir, "enigma.metadata.txt"))
}

if (!file.exists(file.path(enigma_dir, "enigma.otu_table_resampled_updated_r.txt.gz"))) {
    download.file("https://www.dropbox.com/s/u9qh86cd7c0vbn9/enigma.otu_table_resampled_updated_r.txt.gz?dl=1",
                  destfile = file.path(enigma_dir, "enigma.otu_table_resampled_updated_r.txt.gz"))
}
```

```{r enigma-readdata}
## load OTU table and metadata
otu <- read.table(file.path(enigma_dir, "enigma.otu_table_resampled_updated_r.txt.gz"), 
                  sep='\t', header = TRUE, row.names = 1)
meta <- read.csv(file.path(enigma_dir, "enigma.metadata.txt"), sep='\t')
